Large and Infinitary Quotient Inductive-Inductive Types

### 2019-12-28 draft/paper.tex
paper

@@

\newcommand{\bCon}{\boldsymbol{\Con}}
\newcommand{\bTy}{\boldsymbol{\Ty}}
\newcommand{\bSub}{\boldsymbol{\Sub}}
\newcommand{\bTm}{\boldsymbol{\Tm}}
\newcommand{\bGamma}{\boldsymbol{\Gamma}}
\newcommand{\bDelta}{\boldsymbol{\Delta}}
\newcommand{\bsigma}{\boldsymbol{\sigma}}
\newcommand{\bdelta}{\boldsymbol{\delta}}
\newcommand{\bt}{\boldsymbol{t}}
\newcommand{\bu}{\boldsymbol{u}}
\newcommand{\bA}{\boldsymbol{A}}
\newcommand{\bB}{\boldsymbol{B}}
\newcommand{\bid}{\boldsymbol{\id}}

@@

We use Sterling's cumulative algebraic type theory \cite{sterling2019algebraic} as basis for our metatheory. \todo{REASONS}

@@

From now on, we refer to this theory as cETT (cumulative extensional type
theory). When working in cETT, we use the following notation. We have
Russell-style universes $\Set_i$ indexed by natural numbers, dependent functions
as $(x : A)\ra B$, and dependent pairs as $(x : A)\times B$ with projections
$\proj1$ and $\proj2$. We also use subscripts as a field projection notation for
iterated pairs. For example, for $t : (A : \Set_i) \times (B : \Set_i) \times (f
: A \ra B)$, we use $B_t$ to denote the projection of the second
component. Sometimes we omit the subscript if it is clear from context.

@@

@@

\begin{definition}[Finite limit CwFs]\label{def:flCwF}
For a level $i$, there is a cETT type $\flCwF_i : \Set_{i+1}$, which is an
iterated $\Sigma$-type with the following components:
\begin{enumerate}
  \item A CwF with underlying sets all in $\Set_i$. We reuse the notation
    from definition \ref{def:tos}.
  \item $\Sigma$-type $\Sg : (A : \Ty\,\Gamma)\ra \Ty\,(\Gamma \ext A)
    \ra \Ty\,\Gamma$, with term formers $\proj1$, $\proj2$ and $\blank,\blank$.
  \item Identity type $\Id : (A : \Ty\,\Gamma)\ra \Tm\,\Gamma\,A\ra
    \Tm\,\Gamma\,A\ra \Ty\,\Gamma$, with equality reflection and UIP.
  \item Constant families. This includes a type former $\Kfam : \Con \ra
    \Ty\,\Gamma$, where $\Gamma$ is implicitly quantified, and an isomorphism
    between $\Sub\,\Gamma\,\Delta$ and $\Tm\,\Gamma\,(\Kfam\,\Delta)$ which is
    natural in $\Gamma$. We have $\lamK : \Sub\,\Gamma\,\Delta \ra
    \Tm\,\Gamma\,(\Kfam\,\Delta)$ and $\appK : \Tm\,\Gamma\,(\Kfam\,\Delta)
    \ra \Sub\,\Gamma\,\Delta$ as its components.  The idea is that
    $\Kfam\,\Delta$ is a representation of $\Delta$ as a type in any
    context. Clairambault and Dybjer called constant families ``democracy'' in
    \cite{clairambault2014biequivalence}.
\end{enumerate}
\end{definition}

@@

The reason for the ``finite limit CwF'' naming is the following: Clairambault
and Dybjer showed that the 2-category of flCwFs is biequivalent to the
2-category of finitely complete (or ``lex'') categories
\cite{clairambault2014biequivalence}. It can be also seen that the categorical
product of $\Gamma$ and $\Delta$ in an flCwF can be given as $\Gamma \ext
\Kfam\, \Delta$, and equalizers can be given using the identity type.

@@

\begin{definition}[Type categories, c.f.\ \cite{clairambault2014biequivalence}] For each $\Gamma : \Con$, there is a category
whose objects are types $A : \Ty\,\Gamma$, and morphisms from $A$ to $B$ are
terms $t : \Tm\,(\Gamma\,\ext\,A)\,B[\p]$. Identity morphisms are given by $\q :
\Tm\,(\Gamma\,\ext\,A)\,A[\p]$, and composition $t \circ u$ by $t[\p, u]$. The
assignment of type categories to contexts extends to an indexed category. For
each $\sigma : \Sub\,\Gamma\,\Delta$, there is a functor from $\Ty\,\Delta$ to
$\Ty\,\Gamma$, which sends $A$ to $A[\sigma]$ and $t :
\Tm\,(\Gamma\,\ext\,A)\,B[\p]$ to $t[\sigma\circ \p, \q]$.
\end{definition}

@@

\begin{definition} A weak flCwF morphism $\boldsymbol{\sigma : \Sub\,\Gamma\,\Delta}$ is a functor between underlying categories, which additionally maps types to types and terms to terms, and satisfies the following:
  \begin{enumerate}
    \item $\bsigma\,(A[\sigma]) = (\bsigma\,A)\,[\bsigma\,\sigma]$
    \item $\bsigma\,(t[\sigma]) = (\bsigma\,t)\,[\bsigma\,\sigma]$
    \item The unique map $\epsilon : \Sub\,(\bsigma\,\emptycon)\,\emptycon$ has a retraction.
    \item Each $(\bsigma\,\p,\,\bsigma\,\q) : \Sub\,(\bsigma\,(\Gamma\,\ext\,A))\,(\bsigma\,\Gamma\,\ext\,\bsigma\,A)$ has an inverse.
  \end{enumerate}
\end{definition}

In short, $\bsigma$ preserves substitution strictly and preserves
empty context and context extension up to isomorphism. We notate the evident
isomorphisms as $\bsigma_{\emptycon} :
\bsigma\,\emptycon \simeq \emptycon$ and $\bsigma_{\ext}
:
\bsigma\,(\Gamma\,\ext\,A)\,\simeq\,\bsigma\,\Gamma\,\ext\,\bsigma\,A$.

@@

\begin{theorem} Every $\boldsymbol{\sigma : \Sub\,\Gamma\,\Delta}$ preserves fl-structure up to type isomorphism. That is, we have isomorphisms
\begin{alignat*}{3}
  & \bsigma_{\Sigma} : \bsigma\,(\Sigma\,A\,B) \simeq \Sigma\,(\bsigma\,A)\,((\bsigma\,B)[\bsigma_{\ext}^{-1}]) \\
  & \bsigma_{\K} : \bsigma\,(\K\,\Delta) \simeq \K\,(\bsigma\,\Delta) \\
  & \bsigma_{\Id} : \bsigma\,(\Id\,t\,u) \simeq \Id\,(\bsigma\,t)\,(\bsigma\,u)
\end{alignat*}
Moreover, $\bsigma$ preserves all term and substitution formers in the
fl-structure. For example, $\bsigma\,(\proj1\,t) = \proj1\,
(\bsigma_{\Sigma}[\id, \bsigma\,t])$.
\end{theorem}
\begin{proof}
For $\bsigma_{\Sigma}$, we construct the following context isomorphism:
\begin{alignat*}{3}
& (\bsigma\,\Gamma\,\ext\,\bsigma\,(\Sigma\,A\,B)) \simeq
  (\bsigma\,\Gamma\,\ext\,\bsigma\,A\,\ext\,(\Sigma\,B)[\bsigma_{\ext}^{-1}]) \\
& \simeq (\bsigma\,\Gamma\,\ext\,\Sigma\,(\bsigma\,A)\,((\Sigma\,B)[\bsigma_{\ext}^{-1}]))
\end{alignat*}
This isomorphism is the identity on $\bsigma\,\Gamma$, hence we can extract the
desired $\bsigma_{\Sigma} : \bsigma\,\Sigma\,A\,B) \simeq
\Sigma\,(\bsigma\,A)\,((\bsigma\,B)[\bsigma_{\ext}^{-1}])$ from it.

@@

For $\bsigma_{\Id}$, both component morphisms can be constructed by $\refl$ and
equality reflection, and the morphisms are inverses by UIP. We omit here the
verification that $\bsigma$ preserves term and substitution formers.
\end{proof}

@@

%% $\bid : \bSub\,\bGamma\,\bGamma$ is defined in the obvious way, with $\bid
%% For composition

>>>>

\usepackage{tikz-cd}

\newtheorem{notation}{Notation}

@@

\newcommand{\bCon}{\boldsymbol{\Con}}
\newcommand{\bTy}{\boldsymbol{\Ty}}
\newcommand{\bSub}{\boldsymbol{\Sub}}
\newcommand{\bTm}{\boldsymbol{\Tm}}
\newcommand{\bGamma}{\boldsymbol{\Gamma}}
\newcommand{\bDelta}{\boldsymbol{\Delta}}
\newcommand{\bsigma}{\boldsymbol{\sigma}}
\newcommand{\bdelta}{\boldsymbol{\delta}}
\newcommand{\bepsilon}{\boldsymbol{\epsilon}}
\newcommand{\bt}{\boldsymbol{t}}
\newcommand{\bu}{\boldsymbol{u}}
\newcommand{\bA}{\boldsymbol{A}}
\newcommand{\bB}{\boldsymbol{B}}
\newcommand{\bid}{\boldsymbol{\id}}
\newcommand{\bemptycon}{\boldsymbol{\emptycon}}

\newcommand{\ul}[1]{\underline{#1}}
\newcommand{\ulGamma}{\ul{\Gamma}}
\newcommand{\ulDelta}{\ul{\Delta}}
\newcommand{\ulsigma}{\ul{\sigma}}
\newcommand{\uldelta}{\ul{\delta}}
\newcommand{\ulepsilon}{\ul{\epsilon}}
\newcommand{\ult}{\ul{t}}
\newcommand{\ulu}{\ul{u}}
\newcommand{\ulA}{\ul{A}}
\newcommand{\ulB}{\ul{B}}

\newcommand{\coe}{\mathsf{coe}}
\newcommand{\coh}{\mathsf{coh}}

@@

We use Sterling's cumulative algebraic type theory \cite{sterling2019algebraic} as basis for our metatheory. \todo{REASONS, revamp}

@@

From now on, we refer to this theory as cETT (cumulative extensional type
theory). When working in cETT, we use the following notation. We have
Russell-style universes $\Set_i$ indexed by natural numbers, dependent functions
as $(x : A)\ra B$, and dependent pairs as $(x : A)\times B$ with projections
$\proj1$ and $\proj2$. We sometimes leave parameters implicit in dependent
function types, e.g.\ write $\id : A \ra A$ instead of $\id : (A : \Set_i)\ra A
\ra A$. We also use subscripts as a field projection notation for iterated
pairs. For example, for $t : (A : \Set_i) \times (B : \Set_i) \times (f : A \ra
B)$, we use $B_t$ to denote the projection of the second component. Sometimes we
omit the subscript if it is clear from context. When we write ``exists'' in this
paper, we always mean chosen structure given by a $\Sigma$-type.

@@

\todo{compactify cumulativity}

@@

\begin{definition}[Finite limit CwFs]\label{def:flCwF}
For a level $i$, there is a cETT type $\flCwF_i : \Set_{i+1}$, which is an
iterated $\Sigma$-type with the following components:
\begin{enumerate}
  \item A CwF with underlying sets all in $\Set_i$. We reuse the notation
    from definition \ref{def:tos}.
  \item $\Sigma$-type $\Sg : (A : \Ty\,\Gamma)\ra \Ty\,(\Gamma \ext A)
    \ra \Ty\,\Gamma$, with term formers $\proj1$, $\proj2$ and $\blank,\blank$.
  \item Identity type $\Id : (A : \Ty\,\Gamma)\ra \Tm\,\Gamma\,A\ra
    \Tm\,\Gamma\,A\ra \Ty\,\Gamma$, with $\refl$, equality reflection and UIP.
  \item Constant families. This includes a type former $\Kfam : \Con \ra
    \Ty\,\Gamma$, where $\Gamma$ is implicitly quantified, together with $\lamK
    : \Sub\,\Gamma\,\Delta \ra \Tm\,\Gamma\,(\Kfam\,\Delta)$ and its inverse
    $\appK$. The idea is that $\Kfam\,\Delta$ is a representation of $\Delta$ as
    a type in any context. Clairambault and Dybjer called constant families
    ``democracy'' in \cite{clairambault2014biequivalence}.
\end{enumerate}
\end{definition}

@@

The reason for the ``finite limit CwF'' naming is the following: Clairambault
and Dybjer showed that the 2-category of flCwFs is biequivalent to the
2-category of finitely complete categories
\cite{clairambault2014biequivalence}. In particular, in an flCwF the categorical
product of $\Gamma$ and $\Delta$ can be given as $\Gamma \ext \Kfam\, \Delta$,
and the equalizer of $\sigma$ and $\delta$ as $\Gamma\ext
\Id\,(\K\,\Delta)\,(\lamK\,\sigma)\,(\lamK\,\delta)$.

@@

\begin{definition}[Type categories, c.f.\ \cite{clairambault2014biequivalence}]\label{def:type_categories} For each $\Gamma : \Con$, there is a category
whose objects are types $A : \Ty\,\Gamma$, and morphisms from $A$ to $B$ are
terms $t : \Tm\,(\Gamma\,\ext\,A)\,B[\p]$. Identity morphisms are given by $\q :
\Tm\,(\Gamma\,\ext\,A)\,A[\p]$, and composition $t \circ u$ by $t[\p, u]$. The
assignment of type categories to contexts extends to a split indexed category. For
each $\sigma : \Sub\,\Gamma\,\Delta$, there is a functor from $\Ty\,\Delta$ to
$\Ty\,\Gamma$, which sends $A$ to $A[\sigma]$ and $t :
\Tm\,(\Gamma\,\ext\,A)\,B[\p]$ to $t[\sigma\circ \p, \q]$.
\end{definition}

@@

\begin{definition} A \emph{weak flCwF morphism} $\boldsymbol{\sigma : \Sub\,\Gamma\,\Delta}$ is a functor between underlying categories, which additionally maps types to types and terms to terms, and satisfies the following:
  \begin{enumerate}
    \item $\bsigma\,(A[\sigma]) = (\bsigma\,A)\,[\bsigma\,\sigma]$
    \item $\bsigma\,(t[\sigma]) = (\bsigma\,t)\,[\bsigma\,\sigma]$
    \item The unique map $\epsilon : \Sub\,(\bsigma\,\emptycon)\,\emptycon$ has a retraction.
    \item Each $(\bsigma\,\p,\,\bsigma\,\q) : \Sub\,(\bsigma\,(\Gamma\,\ext\,A))\,(\bsigma\,\Gamma\,\ext\,\bsigma\,A)$ has an inverse.
  \end{enumerate}
\end{definition}

In short, $\bsigma$ preserves substitution strictly and preserves
empty context and context extension up to isomorphism. We notate the evident
isomorphisms as $\bsigma_{\emptycon} :
\bsigma\,\emptycon \simeq \emptycon$ and $\bsigma_{\ext}
:
\bsigma\,(\Gamma\,\ext\,A)\,\simeq\,\bsigma\,\Gamma\,\ext\,\bsigma\,A$. Our notion of weak morphism is the same as in \cite{birkedal2018modal}, when restricted to CwFs.

@@

\begin{theorem} Every $\boldsymbol{\sigma : \Sub\,\Gamma\,\Delta}$ preserves fl-structure up to type isomorphism. That is, we have
\begin{alignat*}{3}
  & \bsigma_{\Sigma} : \bsigma\,(\Sigma\,A\,B) \simeq \Sigma\,(\bsigma\,A)\,((\bsigma\,B)[\bsigma_{\ext}^{-1}]) \\
  & \bsigma_{\K} : \bsigma\,(\K\,\Delta) \simeq \K\,(\bsigma\,\Delta) \\
  & \bsigma_{\Id} : \bsigma\,(\Id\,t\,u) \simeq \Id\,(\bsigma\,t)\,(\bsigma\,u)
\end{alignat*}
Moreover, $\bsigma$ preserves all term and substitution formers in the
fl-structure. For example, $\bsigma\,(\proj1\,t) = \proj1\,
(\bsigma_{\Sigma}[\id, \bsigma\,t])$.
\end{theorem}
\begin{proof}
For $\bsigma_{\Sigma}$, we construct the following context isomorphism:
\begin{alignat*}{3}
& (\bsigma\,\Gamma\,\ext\,\bsigma\,(\Sigma\,A\,B)) \simeq
  (\bsigma\,\Gamma\,\ext\,\bsigma\,A\,\ext\,(\Sigma\,B)[\bsigma_{\ext}^{-1}]) \\
& \simeq (\bsigma\,\Gamma\,\ext\,\Sigma\,(\bsigma\,A)\,((\Sigma\,B)[\bsigma_{\ext}^{-1}]))
\end{alignat*}
This isomorphism is the identity on $\bsigma\,\Gamma$, hence we can extract the
desired $\bsigma_{\Sigma} : \bsigma\,\Sigma\,A\,B) \simeq
\Sigma\,(\bsigma\,A)\,((\bsigma\,B)[\bsigma_{\ext}^{-1}])$ from it.

@@

For $\bsigma_{\Id}$, both component morphisms can be constructed by $\refl$ and
equality reflection, and the morphisms are inverses by UIP. We omit here the
verification that $\bsigma$ preserves term and substitution formers in the
fl-structure.
\end{proof}

@@

$\bid : \bSub\,\bGamma\,\bGamma$ is defined in the obvious way, with identities for
underlying functions and for preservation morphisms.

For $\boldsymbol{\sigma \circ \delta}$, the underlying functions are given by
function composition, and the preservation morphisms are given as follows:
\begin{alignat*}{3}
  & (\boldsymbol{\sigma \circ \delta})_{\emptycon}^{-1} :\equiv
    \bsigma\,\bdelta_{\emptycon}^{-1} \circ \bdelta_{\emptycon}^{-1} \\
  & (\boldsymbol{\sigma \circ \delta})_{\ext}^{-1} :\equiv
    \bsigma\,\bdelta_{\ext}^{-1} \circ \bdelta_{\ext}^{-1}
\end{alignat*}

\begin{lemma} The derived preservation isomorphisms for the fl-structure can be decomposed analogously; all derived isomorphisms in $\bid$ are identities, and we have
\begin{alignat*}{3}
  & (\boldsymbol{\sigma \circ \delta})_{\Sigma} =
  \bsigma\,\bdelta_{\Sigma} \circ \bdelta_{\Sigma}\\
  & (\boldsymbol{\sigma \circ \delta})_{\K} =
  \bsigma\,\bdelta_{\K} \circ \bdelta_{\K}\\
  & (\boldsymbol{\sigma \circ \delta})_{\Id} =
  \bsigma\,\bdelta_{\Id} \circ \bdelta_{\Id}
\end{alignat*}
Here, $\blank\circ\blank$ denotes composition of type morphisms.
\end{lemma}
\begin{proof} In the case of $\Id$, the equations hold immediately by UIP. For $\Sigma$ and $\K$, we prove by flCwF computation and straightforward unfolding of definitions.
\end{proof}

\subsection{Empty Context}
The empty context $\boldsymbol{\emptycon : \Con}$ is the terminal flCwF, which
has all underlying sets defined as $\top$ (or constantly $\top$), with an
evident unique $\boldsymbol{\epsilon : \Sub\,\Gamma\,\emptycon}$. Since
$\bepsilon$ is a strict flCwF morphism, $\bepsilon_{\emptycon}^{-1}$ and
$\bepsilon_{\ext}^{-1}$ are both identity morphisms.

\subsection{Types}

We define $\boldsymbol{\Ty\,\Gamma} : \Set_{1 + \max(i, j+1)}$ as the type of
split flCwF-isofibrations over $\bGamma$. We extend Ahrens' and Lumsdaine's
displayed categories and their definition of isofibrations \cite{displayedcats}.
We first define displayed flCwFs, then specify iso-cleaving as additional structure
on top of that.

\begin{definition}[Displayed flCwF] The type of displayed flCwFs is given as the logical predicate interpretation \cite{TODO} of $\flCwF_i$. For each flCwF component in $\bGamma$, there is a component in a displayed flCwF which ``lies over'' it.

In situations where we need to refer to both ``base'' and displayed things, we give
\ul{underlined} names to contexts, substitutions, types and terms in a base
flCwF. For example, we may have $\ulGamma : \Con_{\bGamma}$ living in
$\boldsymbol{\Gamma : \Con}$, and $\Gamma : \Con_{\bA}\,\ulGamma$ living in
$\boldsymbol{A : \Ty\,\Gamma}$. We only use underlining on cETT variable names,
and overload flCwF component names for displayed counterparts.

Concretely, $\boldsymbol{A : \Ty\,\Gamma}$ has the following underlying sets, which we call displayed contexts, substitutions, types and terms respectively.
\begin{alignat*}{3}
  & \Con_{\bA} && : \Con_{\bGamma}\ra \Set_i\\
  & \Sub_{\bA} && : \Con_{\bA}\,\ulGamma \ra \Con_{\bA}\,\ulDelta \ra \Sub_{\bGamma}\,\ulGamma\,\ulDelta \ra \Set_i \\
  & \Ty_{\bA}  && : \Con_{\bA}\,\ulGamma \ra \Ty_{\bGamma}\,\ulGamma \ra \Set_i\\
  & \Tm_{\bA}  && : (\Gamma : \Con_{\bA}\,\ulGamma)\ra \Ty_{\bA}\,\Gamma\,\ulA \ra \Tm_{\bGamma}\,\ulGamma\,\ulA \ra \Set_i
\end{alignat*}

Above, we implicitly quantify over $\ulGamma$, $\ulDelta$ and $\ulA$ base
parameters. We also have the following components for empty context, context
extension and substitution. We omit listing other components here.
\begin{alignat*}{3}
  & \emptycon_{\bA} && : \Con_{\bA}\,\emptycon_{\bGamma}\\
  & \ext_{\bA}      && : (\Gamma : \Con_{\bA}\,\ulGamma)\ra \Ty_{\bA}\,\Gamma\,\ulA \ra
                     \Con_{\bA}\,\Gamma\,(\ulGamma \ext_{\bGamma} \ulA)\\
  & \blank[\blank]_{\bA} && : \Ty_{\bA}\,\Delta\,\ulA \ra \Sub_{\bA}\,\Gamma\,\Delta\,\ulsigma
                     \ra \Ty_{\bA}\,\Gamma\, (\ulA[\ulsigma]_{\bGamma})\\
  & \blank[\blank]_{\bA} && : \Tm_{\bA}\,\Delta\,A\,\ult \ra (\sigma : \Sub_{\bA}\,\Gamma\,\Delta\,\ulsigma)\\
  & && \hspace{0.5em}\ra \Tm_{\bA}\,\Gamma\, (A[\sigma]_{\bA})\,(\ult[\ulsigma]_{\bGamma})
\end{alignat*}
\end{definition}

In the following we will often omit $_{\bGamma}$ and $_{\bA}$ subscripts on
components; for example, in the type $\Con_{\bA}\,\emptycon$, the $\emptycon$ is clearly
a base component in $\bGamma$.

We also need displayed counterparts to the previously defined derived notions on flCwFs;
these are again given as logical predicate interpretations of the non-displayed definitions.

\begin{definition}[Displayed type categories] For each $\Gamma : \Con_{\bA}\,\ulGamma$, there
is a displayed category over the type category $\Ty_{\bGamma}\,\ulGamma$, whose objects
over $\ulA : \Ty_{\bGamma}\,\ulGamma$ are elements of $\Ty_{\bA}\,\Gamma\,\ulA$, and displayed morphisms over $\ult : \Tm_{\bGamma}\,(\ulGamma \ext \ulA)\,(\ulB[\p])$ are elements of $\Tm_{\bA}\,(\Gamma \ext A)\,(B[\p])\,\ult$. The identity morphism is given by $\q_{\bA}$, and the composition of $t$ and $u$ is $t[\p_{\bA},u]$. Analogously to Definition \ref{def:type_categories}, this extends to a displayed split indexed category.
\end{definition}

\begin{definition}[Displayed isomorphisms] A \emph{displayed context isomorphism} over $\ulsigma : \ulGamma \simeq \ulDelta$, notated $\sigma : \Gamma \simeq_{\ulsigma} \Delta$, is an invertible displayed morphism $\sigma : \Sub_{\bA}\,\Gamma\,\Delta\,\ulsigma$, with inverse $\sigma^{-1} : \Sub_{\bA}\,\Delta\,\Gamma\,\ulsigma^{-1}$. A \emph{displayed type isomorphism} over $\ult : \ulA \simeq \ulB$, notated $t : A \simeq_{\ult} B$, is an isomorphism in a displayed type category.
\end{definition}

\begin{definition} A \emph{vertical morphism} lies over an identity morphism. We use this definition for context and type morphisms as well.
\end{definition}

In contrast to \cite{kaposi2019constructing}, it is not sufficient to model
types with displayed flCwFs. In ibid.\ substitutions are modeled as strict
morphisms, which we cannot do because our infinitary function types and identity
types cannot be interpreted strictly, as we will see in Section
\ref{TODO}. Strict preservation is expressed with metatheoretic equality, which
is respected by all cETT constructions, but isomorphisms are not necessarily
respected. Hence, we need to add additional structure to displayed flCwFs which
expresses preservation of base isomorphisms.

\begin{definition}[Context iso-cleaving] This lifts a base context isomorphism to a displyed one. It consists of
\begin{alignat*}{3}
  & \coe : \ulGamma \simeq \ulDelta \ra \Con_{\bA}\,\ulGamma \ra \Con_{\bA}\,\ulDelta\\
  & \coh : (\ulsigma : \ulGamma \simeq \ulDelta)(\Gamma : \Con_{\bA}\,\ulGamma)
           \ra \Gamma \simeq_{\ulsigma} \coe\,\ulsigma\,\Gamma
\end{alignat*}
such that
\begin{alignat*}{3}
  & \coe\,\id\,\Gamma && = \Gamma\\
  & \coe\,(\ulsigma\circ\uldelta)\,\Gamma && = \coe\,\ulsigma\,(\coe\,\uldelta\,\Gamma)\\
  & \coh\,\id\,\Gamma && = \id\\
  & \coh\,(\ulsigma\circ\uldelta)\,\Gamma && = \coh\,\ulsigma\,(\coe\,\uldelta\,\Gamma)
          \circ \coh\,\uldelta\,\Gamma
\end{alignat*}
Here, $\coe$ and $\coh$ abbreviate ``coercion'' and ``coherence'' respectively.
\end{definition}

\begin{definition}[Type iso-cleaving] This consists of
\begin{alignat*}{3}
  & \coe : \ulA \simeq \ulB \ra \Ty_{\bA}\,\Gamma\,\ulA \ra \Ty_{\bA}\,\Gamma\,\ulB\\
  & \coh : (\ult : \ulA \simeq \ulB)(A : \Ty_{\bA}\,\Gamma\,\ulA)
           \ra A \simeq_{\ult} \coe\,\ult\,A
\end{alignat*}
such that
\begin{alignat*}{3}
  & \coe\,\id\,A && = A\\
  & \coe\,\ult\,(\coe\,\uldelta\,A) && = \coe\,(\ult\circ\uldelta)\,A\\
  & \coh\,\id\,A && = \id\\
  & \coh\,(\ult\circ\uldelta)\,A && = \coh\,\ult\,(\coe\,\uldelta\,A)
          \circ \coh\,\uldelta\,A
\end{alignat*}
Also, whenever $\sigma : \Sub_{\bA}\,\Gamma\,\Delta\,\ulsigma$, we have
\begin{alignat*}{3}
  & \coe\,(\ult[\ulsigma])\,(A[\sigma]) && = (\coe\,\ult\,A)[\sigma]\\
  & \coh\,(\ult[\ulsigma\circ \p,\q])\,(A[\sigma]) && = (\coh\,\ult\,A)[\sigma]
\end{alignat*}

\end{definition}

\begin{definition} A \emph{split flCwF isofibration} is a displayed flCwF equipped with iso-cleaving for contexts and types.
\end{definition}

\subsection{Type Substitution}

We seek to define $\boldsymbol{\blank[\blank] : \Ty\,\Delta \ra \Sub\,\Gamma\,\Delta \ra \Ty\,\Gamma}$.
